\documentclass[10pt, a4paper]{article}

%---- Required Packages ----
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{lmodern}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{xcolor}

\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{%
  \vspace{0.6mm}%
  \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}%
      \textbf{#1} & \footnotesize{#4} \\%
    \footnotesize{#3} & \fontsize{9}{10}\selectfont#2%
  \end{tabular*}%
  \vspace{-2.4mm}%
}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

\vspace*{-1.0cm}

%----------HEADING----------
\begin{center}
    {\fontsize{22}{24}\selectfont\textbf{KARTHIKEYA KALLAPU}} \\[4pt]
    \small
    \faPhone~+91-9440903979 \hspace{1pt} $|$
    \faEnvelope~\href{mailto:karthikeyakallapu@gmail.com}{karthikeyakallapu@gmail.com} \hspace{1pt} $|$
    \faGlobe~\href{https://karthikeyakallapu.vercel.app}{karthikeyakallapu.vercel.app} \hspace{1pt} $|$
    \faGithub~\href{https://github.com/karthikeyakallapu}{github.com/karthikeyakallapu} \hspace{1pt} $|$
    \faLinkedin~\href{https://linkedin.com/in/karthikeyakallapu}{linkedin.com/in/karthikeyakallapu}
    \\ \vspace{-3pt}
\end{center}

\vspace{0.2cm}

% ---------------- EDUCATION ----------------
\section{\textbf{EDUCATION}}

\resumeSubheading
{CMR College of Engineering and Technology, Hyderabad.}{ 2020 - 2024 }
{Bachelor of Technology in Computer Science and Engineering (Cyber Security)}{CGPA: \textbf{8.81}}

\vspace{-3.0mm}

% ---------------- EXPERIENCE ----------------
\section{\textbf{EXPERIENCE}}

\resumeSubheading
{Software Engineer}{ July 2024 - Present }{
  Planful, Inc.
}{}

\begin{itemize}[itemsep=-5pt]
  \item Developed UI and API automation frameworks, reducing overall test execution time by \textbf{73}\%.
  \item Migrated automation test results from local storage to a centralized database and built UI dashboards to analyze execution metrics across multiple environments.
\end{itemize}

\vspace{-3.0mm}

\resumeSubheading
{Software Engineering Intern}{ Dec 2023 - June 2024 }{
  Planful, Inc.
}{}

\begin{itemize}[itemsep=-5pt]
  \item Conducted a proof of concept on various UI automation tools, selecting pywinauto for Excel UI automation and contributing to API automation efforts.
\end{itemize}

% ---------------- PROJECTS ----------------
\vspace{-3.0mm}
\section{\textbf{PROJECTS}}

\resumeSubheading
{Tunemate \fontsize{9}{9}\selectfont\fontseries{l}\selectfont - React.js, Tailwind CSS, Zustand, Node.js, Express.js, Redis, Prisma, MongoDB, Web Sockets.}{} {}{}
\vspace{-4.2mm}

\begin{itemize}[itemsep=-4pt]
  \item Built a real-time collaborative music platform using WebSockets and Redis, enabling synchronized playback actions such as play, pause, and seek with low latency.
  \item Increased user engagement by implementing custom playlist creation and interactive listening experiences across connected users.
  \item \textbf{Project: } \href{https://github.com/ikarthik21/tunemate}{GitHub} - \href{https://tunemate.vercel.app/}{Live}
\end{itemize}

\vspace{-2.0mm}

\resumeSubheading
{E-Restaurant \fontsize{9}{9}\selectfont\fontseries{l}\selectfont - React.js, Express.js, Node.js, MongoDB, Razorpay.}{} {}{}
\vspace{-4.2mm}

\begin{itemize}[itemsep=-4pt]
  \item Digitized a restaurant system with a manual-to-digital conversion, resulting in a reduction in wait times and an increase in overall efficiency.
  \item Facilitated rapid customer transactions, enabling users to register, book tables, order food, and make payments in an average of \textbf{3} minutes.
  \item Streamlined table bookings and order processing, reducing admin workload and ensuring seamless customer experiences.
  \item \textbf{Project: } \href{https://github.com/ikarthik21/RestobayFoods}{GitHub} - \href{https://restobayfoods.vercel.app/}{Live}
\end{itemize}

\vspace{-2.0mm}

\resumeSubheading
{ESBOX \fontsize{9}{9}\selectfont\fontseries{l}\selectfont - React.js, Tailwind CSS, FastAPI, PostgreSQL, Redis, Docker, Nginx.}{} {}{}
\vspace{-4.2mm}

\begin{itemize}[itemsep=-4pt]
  \item Built a secure cloud-based file storage and sharing platform supporting file uploads, downloads, and workspace-based collaboration for registered users.
  \item Designed backend services using FastAPI with streaming-based file handling to efficiently serve large files without loading them fully into memory.
  \item Implemented Redis-based locking to manage concurrent operations and integrated shareable links for controlled file access.
  \item Deployed the platform using Docker, Nginx, and CI/CD pipelines for automated builds and deployments.
  \item \textbf{Project: } \href{https://github.com/karthikeyakallapu/esbox}{GitHub}
\end{itemize}

% ---------------- SKILLS ----------------
\vspace{-3.5mm}
\section{\textbf{TECHNICAL SKILLS}}

\resumeSubheading
{Languages: \fontsize{11.5}{11.5}\selectfont\fontseries{l}\selectfont C, C++, JavaScript, Python}{}{}{}
\vspace{-5.15mm}

\resumeSubheading
{Frontend: \fontsize{11.5}{11.5}\selectfont\fontseries{l}\selectfont HTML, CSS, Tailwind CSS, React.js, Next.js, Zustand.}{}{}{}
\vspace{-5.15mm}

\resumeSubheading
{Backend: \fontsize{11.5}{11.5}\selectfont\fontseries{l}\selectfont Node.js, Express.js, REST APIs, FastAPI, SQLAlchemy, Alembic.}{}{}{}
\vspace{-5.15mm}

\resumeSubheading
{Databases: \fontsize{11.5}{11.5}\selectfont\fontseries{l}\selectfont PostgreSQL, MySQL, MongoDB, Redis.}{}{}{}
\vspace{-5.15mm}

\resumeSubheading
{Tools \& Platforms: \fontsize{11.5}{11.5}\selectfont\fontseries{l}\selectfont Docker, Git, GitHub, Postman.}{}{}{}

% ---------------- ACHIEVEMENTS ----------------
\vspace{-5.0mm}
\section{\textbf{ACHIEVEMENTS}}

\begin{itemize}[itemsep=-4pt]
  \item Received Spot Award at Planful for outstanding contributions in Excel UI automation.
  \item Implemented automation script for smoke tests achieving a \textbf{73}\% reduction in execution time.
  \item Secured a global rank of 154 in Code Chef Starters 71.
\end{itemize}

\end{document}